\vspace{-2.75cm}Technological Change and U.S. Foreign Aid\vspace{-0.5cm}

### 2022-12-08 Paper.tex

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\title{\vspace{-2.75cm}Conflating Global Finance with Technological Competition: The U.S.'s Reaction to Chinese Foreign Aid\vspace{-0.5cm}}
\author{Nicholas Ray}
\date{\vspace{-0.30cm}December 7 2022\vspace{-1cm}}
\usepackage[margin=1in]{geometry}
\usepackage{mathtools,amssymb,amsthm}
\usepackage{setspace}
\doublespacing
\usepackage{footmisc}
\renewcommand{\footnotelayout}{\setstretch{1.75}}
\usepackage{footmisc}
\renewcommand{\footnotesize}{\normalsize}
\usepackage{caption}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,fit,positioning,shapes.symbols,chains}
\usepackage{blindtext}
\usepackage{istgame}
\usepackage[backend=biber, style=authoryear, maxbibnames=99,uniquelist=false]{biblatex}
\renewbibmacro{in:}{}
\renewbibmacro*{volume+number+eid}{%
  \printfield{volume}
  \setunit*{\addnbthinspace}
  \printfield{number}
  \setunit{\addcomma\space}
  \printfield{eid}}
\DeclareFieldFormat[article]{number}{\mkbibparens{#1}}
\AtEveryBibitem{
  \clearfield{issn}
  \clearfield{month}
  \clearfield{urlyear}
  \clearlist{language}
  \clearfield{note}
  \clearfield{month}
  \clearfield{day}
  \ifentrytype{online}{}{
    \clearfield{url}
  }
}
\addbibresource{ForeignAidBib.bib}
\begin{document}
\maketitle
\begin{abstract}
    Emphasize policy! \blindtext
\end{abstract}

@@

\section*{Introduction}
\footnote{All data and code can be found on GitHub at https://github.com/nnray/Analysis. In the ``Code'' folder, navigate to ``628.Rmd'' for my R script. My full \LaTeX \;file can be found at https://github.com/nnray/628 under ``Paper.tex''.}

\section*{What Needs Explaining?}
%U.S. digital infrastructure spending, other aid related to ICT/internet
The U.S. has been increasingly funding digital infrastructure in countries around the world. In 2022, for example, the U.S. initiated the Partnership for Global Infrastructure and Investment (PGII) in collaboration with the other members of the Group of Seven (G7) that aims to spend \$600 billion on global infrastructure projects over the next five years (\cite{thewhitehouse2022}). Included in the PGII is a \$600 million contract to a U.S. telecommunications company to build submarine internet cables that connect Singapore to France via Egypt and the Horn of Africa. %other U.S. examples? IF programs?

%Chinese digital infrastructure spending
This intention of the U.S. to build digital infrastructure closely resembles the behavior of China over the past two decades. Since engaging in their ``going out'' strategy of investing overseas to promote domestic economic growth, China has turned to funding massive infrastructure projects through its Belt and Road Initiative (BRI) and becoming the ``lender of first resort'' for developing countries (\parencite[1]{dreher2022}). Two years after announcing the BRI, China launched the largely symbolic (\cite{tugendhat2021}) Digital Silk Road (DSR) that still encapsulates China's desire to build global digital infrastructure favorable to them (\cite{shen2022}). Some examples of relevant Chinese projects are shown in table 1 \nocite{agbebi2022}.

@@

%the competition between U.S. and Chinese technology, digital infrastructure spending
However, the U.S. and China do not seem to be cooperating in the effort to improve digital infrastructure worldwide. Just months before the PGII announcement, the U.S. pioneered a thinly veiled condemnation of China in the Declaration for the Future of the Internet in which more than 60 countries signed a pledge to engage in liberal internet governance (\cite{u.s.departmentofstate2022}). Further, policy analysts and scholars have a highlighted a U.S. concern over Chinese spending (\cite{hass2021}; \cite{triolo2020}; \cite{hillman2021}). But why exactly is the U.S. attempting to compete with China in foreign spending and why the digital aspect? %need more work here

\section*{Extant Explanations}
For a comprehensive but not exhaustive overview of the literature on foreign aid determinants, see Fuchs, Dreher, and Nunnenkamp 2014 \nocite{fuchs2014} (Table 1, p. 173). Simplistically, the foreign aid literature has explained donor behavior as the result of either recipient need or self-interested motivations, with the self-interested reasons being categorizable as political or economic. Focusing on the determinants of U.S. foreign aid, I argue that the extant explanations do not fully capture either the technology focus of current U.S. aid behavior or the antagonistic nature of said behavior.

@@

\section*{My Explanation}
I contend that an explanation of current U.S. foreign spending behavior that addresses both why it has a strong focus on technology and why this focus seems opposed to China should be based on both political and economic determinants related to technology. Specifically, I argue that the U.S. has a policy preference for more liberal internet governance, or the rules and norms surrounding the internet in a country,  because a liberal internet enables Western technology to operate within that country. That is, I claim that U.S. aid can be described by the political determinant of liberal internet governance and the economic determinant of market access for Western technology firms.

I will next define internet governance and why it is a political determinant for U.S. aid. Internet governance was defined in the second phase of the World Summit on the Information Society (WSIS), a meeting led by the UN's International Telecommunication Union (ITU), which was held in Tunis, Tunisia in 2005. It is ``the development and application by governments, the private sector and civil society, in their respective roles, of shared principles, norms, rules, decision-making procedures, and programmes that shape the evolution and use of the Internet'' \nocite{worldsummitontheinformationsociety2005} (World Summit on the Information Society 2005, item 34). Essentially, internet governance refers to the way in which governments, firms, and citizens interact with the internet.

The U.S. is concerned about internet governance because there is evidence that the West believes China to be spreading its illiberal model of the internet (e.g., \cite{hillman2021}; \cite{u.s.departmentofstate2022}), or at least that there is a good chance for it to (\cite{triolo2020}).

However, I argue that the U.S. focus on internet governance is not simply about the politics of a liberal internet, such as preferences for democracy or human rights. Firstly, according to the literature there is little evidence that U.S. government aid discriminates much along the lines of human rights (\cite{hoeffler2011}) or even democracy (\cite{alesina2000}; \cite{hoeffler2011}). Rather, I argue that the U.S.'s interest in propping up internet governance around the world chiefly lies in the desire to prevent countries of using the internet in a manner similar to China (\cite{hass2021}), which is more likely to occur with the increase in global Chinese spending.

\section*{Implications}
If U.S. foreign spending is truly concerned with internet governance and the economic benefits of inhibiting China's suspected illiberal influence, then it should also be true that the internet governance of potential recipients should be a strong predictor of U.S. foreign aid over time. This implication leads to the following hypothesis:
\begin{align*}
    H_{1}&:\;\text{U.S. aid should be empirically related to recipient internet governance}\\
\end{align*}

\section*{Empirics}
I test this hypotheses by regressing U.S. foreign aid on a measure of internet governance, Chinese aid and controls across 44 African countries between 2010 and 2017. The full set of countries includes: Algeria, Angola, Benin, Botswana, Burundi, Cabo Verde, Cameroon, Central African Republic, Chad, Comoros, Republic of the Congo, Cote d'Ivoire, Democratic Republic of the Congo, Djibouti, Egypt, Equatorial Guinea, Ethiopia, Gabon, Gambia, Ghana, Guinea, Guinea-Bissau, Kenya, Lesotho, Liberia, Madagascar, Malawi, Mali, Mauritania, Mauritius, Morocco, Mozambique, Namibia, Niger, Nigeria, Rwanda, Senegal, Sierra Leone, South Africa, Togo, Tunisia, Uganda, Zambia, and Zimbabwe.

@@

\subsection*{Data and Variables}
%internet freedom
In operationalizing my theory, I measure internet governance as ``internet freedom'' from the Digital Society Project (DSP) index. The DSP aims to identify ``how people use social media as a political tool and to explore how political institutions and social media use interact,'' providing data from expert surveys that cover a range of topics such as censorship, disinformation, and monitoring (\cite{mechkova2022}). The DSP employs methodology designed by the Varieties of Democracy project (V-Dem, \cite{coppedge2022}) to try and estimate differences in expert opinion and knowledge.

@@

%controls
For controls, I include gross domestic product GDP per capita, an indicator for internet development, and a measure for political freedom as controls. Each of these phenomena are possible confounders, being theoretically related to at least one of the types of aid and internet freedom.

@@

Description.
\subsubsection*{Table 3}
\begin{figure}[htbp]
    \includegraphics[scale=0.45]{Figures/summary.png}
\end{figure}

\pagebreak
A correlation matrix of the variables included in my regressions is given in Figure 2. As can be seen, there are a couple relatively strong relationships between the variables. The variable for regime type, Polity, has a correlation of 0.62 with the internet freedom variable while logged GDP per capita has a correlation of 0.65 with the variable representing the percent of the population using the internet. While possible, I do not think that these correlations are high enough to warrant concerns over multicollinearity or the lack of linear independency in the data. Interestingly, logged U.S. Aid appears somewhat negatively correlated with logged GDP per capita and variable for the percent using the internet is somewhat positively correlated to that for internet freedom. However, all of these correlations are relatively small and should not induce concerns for multicollinearity, although I did not conduct a formal test for multicollinearity.

@@

\pagebreak
\section*{Results}
Table 2 displays regression results from a model with and without an interaction between internet freedom and logged Chinese foreign aid.
\subsection*{Table 4}
\begin{table}[!htbp] \centering 
  \caption*{Logged U.S. Aid and Covariates with Two-way Fixed Effects and Clustered SE's on Country}
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{2}{c}{Logged U.S. Aid} \\ 
\cline{2-3} 
 & Model 1 & Model 2 \\ 
\hline \\[-1.8ex] 
 Internet Freedom & 0.021$^{***}$ & 0.021$^{***}$ \\ 
  & (0.008) & (0.008) \\ 
  & & \\ 
 Logged Chinese Aid & 0.006$^{*}$ & 0.006$^{*}$ \\ 
  & (0.003) & (0.003) \\ 
  & & \\ 
 Logged GDP per Capita & 0.045 & 0.045 \\ 
  & (0.471) & (0.472) \\ 
  & & \\ 
 Percent Using Internet & $-$0.013 & $-$0.013 \\ 
  & (0.009) & (0.009) \\ 
  & & \\ 
 Polity & 0.004 & 0.004 \\ 
  & (0.031) & (0.031) \\ 
  & & \\ 
 Internet Freedom $\cdot$ Logged Chinese Aid &  & 0.00000 \\ 
  &  & (0.0002) \\ 
  & & \\ 
\hline \\[-1.8ex] 
Observations & 352 & 352 \\ 
R$^{2}$ & 0.038 & 0.038 \\ 
Adjusted R$^{2}$ & $-$0.140 & $-$0.144 \\ 
F Statistic & 2.370$^{**}$ (df = 5; 296) & 1.968$^{*}$ (df = 6; 295) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}
\pagebreak

The only covariates that appear statistically significant are internet freedom and Chinese spending. Both internet freedom and logged Chinese aid seem to increase logged U.S. aid on average when accounting for the other covariates. To gauge the substantive size of the coefficients, I plot the marginal effect of internet freedom on logged U.S. aid in Figure 3 and the marginal effect of logged Chinese aid on logged U.S. aid in Figure 4.

Support for $H_1$?

Interestingly, there is a lack of support for an interaction between internet freedom and logged Chinese aid. Apparently, the effects of a recipient's internet freedom level and the amount of Chinese aid they are receiving have completely separate effects on U.S. aid. However, it is unclear how consequential this lack of support for the interaction term is, since both variables by themselves are significant and two-way fixed effects are used.

\pagebreak
Figure 3 shows the marginal effect of internet freedom on logged U.S. foreign aid. The coefficient on the internet freedom variable is 0.0206, implying that a one unit increase in a recipient's internet freedom level is associated with an increase in U.S. aid by 2.08 percent on average, accounting for other covariates. This appears to be a substantively large effect.

@@

\section*{Discussion}
Discuss contribution and implications of support for $H_1$ in light of the literature on foreign aid and LIO.

\section*{Conclusion}
In this article I argue that . In particular, .

Analyzing 44 African countries from 2010-2017, I find .

I suggest the following future work: Expanding sample to LA Extending years to 2000 Robustness checks with different measurements Greater differntiation between types of aid and money

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\title{\vspace{-2.75cm}Technological Change and U.S. Foreign Aid\vspace{-0.5cm}}
\author{Nicholas Ray}
\date{\vspace{-0.30cm}December 7 2022\vspace{-1cm}}
\usepackage[margin=1in]{geometry}
\usepackage{mathtools,amssymb,amsthm}
\usepackage{setspace}
\doublespacing
\usepackage{footmisc}
\renewcommand{\footnotelayout}{\setstretch{1.75}}
\usepackage{footmisc}
\renewcommand{\footnotesize}{\normalsize}
\usepackage{caption}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,fit,positioning,shapes.symbols,chains}
\usepackage{blindtext}
\usepackage{istgame}
\usepackage[backend=biber, style=authoryear, maxbibnames=99,uniquelist=false]{biblatex}
\renewbibmacro{in:}{}
\renewbibmacro*{volume+number+eid}{%
  \printfield{volume}
  \setunit*{\addnbthinspace}
  \printfield{number}
  \setunit{\addcomma\space}
  \printfield{eid}}
\DeclareFieldFormat[article]{number}{\mkbibparens{#1}}
\AtEveryBibitem{
  \clearfield{issn}
  \clearfield{month}
  \clearfield{urlyear}
  \clearlist{language}
  \clearfield{note}
  \clearfield{month}
  \clearfield{day}
  \ifentrytype{online}{}{
    \clearfield{url}
  }
}
\addbibresource{ForeignAidBib.bib}
\begin{document}
\maketitle
\begin{abstract}
    I argue that the U.S. is funding digital infrastructure in Africa to prevent the Chinese from building such infrastructure and closing market access to U.S. technology firms. Testing the implications that U.S. foreign aid spending is directly related to a measure for internet governance and inversely related to Chinese aid, I find mixed results in a sample of 44 African countries from 2010-2017. U.S. aid seems directly related to both internet governance and Chinese spending.
\end{abstract}

@@

\section*{Introduction}
The United States (U.S.) has been increasingly funding digital infrastructure in countries around the world.\footnote{All R code, data, and \LaTeX \;code can be found at  underlying my analysis can be found on GitHub at https://github.com/nnray.} Simultaneously, the People's Republic of China (China) has advanced its own digital infrastructure projects and financial assistance to become the ``lender of first resort'' for developing countries in the last decade \parencite[1]{dreher2022}. Available explanations do not sufficiently address this seeming great power competition along digital infrastructure. In this article I put forth an explanation specifying that the U.S. is funding digital infrastructure in Africa to prevent the Chinese from building such infrastructure and closing market access to U.S. technology firms.

I make two contributions in the exploration of this topic. Firstly, I add to the foreign aid literature by detailing a novel determinant of U.S. foreign aid and providing another clue on how Chinese money may have impacted Western donor behavior more generally. Secondly, I speak to literature on the liberal international order (LIO) and the concern that China may undermine tenets of the LIO. %expand on this a bit?

I proceed as follows. In the next section, I introduce puzzling observations of recent U.S. behavior followed by a review of current explanations. After considering these accounts, I introduce my argument its implications. Then, I describe my research design before presenting findings and a discussion of contributions.

\section*{What Needs Explaining}
%U.S. digital infrastructure spending, other aid related to ICT/internet
The U.S. has been increasingly funding digital infrastructure in countries around the world. In 2022, for example, the U.S. initiated the Partnership for Global Infrastructure and Investment (PGII) in collaboration with the other members of the Group of Seven (G7) that aims to spend \$600 billion on global infrastructure projects over the next five years (\cite{thewhitehouse2022}). Included in the PGII is a \$600 million contract to a U.S. telecommunications company to build submarine internet cables that connect Singapore to France via Egypt and the Horn of Africa. %other U.S. examples? IF programs?

%Chinese digital infrastructure spending
This intention of the U.S. to build digital infrastructure closely resembles the behavior of China over the past two decades. Since engaging in their ``going out'' strategy of investing overseas to promote domestic economic growth, China has turned to funding massive infrastructure projects through its Belt and Road Initiative (BRI) and becoming the ``lender of first resort'' for developing countries \parencite[1]{dreher2022}. Two years after announcing the BRI, China launched the largely symbolic (\cite{tugendhat2021}) Digital Silk Road (DSR) that still encapsulates China's desire to build global digital infrastructure favorable to them (\cite{shen2022}). Some examples of relevant Chinese projects are shown in table 1 \nocite{agbebi2022}.

@@

%the competition between U.S. and Chinese technology, digital infrastructure spending
However, the U.S. and China do not seem to be cooperating in the effort to improve digital infrastructure worldwide. Just months before the PGII announcement, the U.S. pioneered a thinly veiled condemnation of China in the Declaration for the Future of the Internet in which more than 60 countries signed a pledge to engage in liberal internet governance (\cite{u.s.departmentofstate2022}). Further, policy analysts and scholars have a highlighted a U.S. concern over Chinese spending (\cite{hass2021}; \cite{triolo2020}; \cite{hillman2021}). Consequently, it appears that the U.S. and China are both separately spending on digital infrastructure projects while the U.S. actively opposes China's doing so.

\section*{Extant Explanations}
There are some tentative explanations offered by the global finance literature for this competitive spending behavior surrounding technology. For a comprehensive but not exhaustive overview of the literature on foreign aid determinants, see Fuchs, Dreher, and Nunnenkamp 2014 \nocite{fuchs2014} (Table 1, p. 173). Simplistically, the foreign aid literature has explained donor behavior as the result of either recipient need or self-interested motivations, with the self-interested reasons being categorizable as political or economic. Focusing on the determinants of U.S. foreign aid, I argue that the extant explanations do not fully capture either the technology focus of current U.S. aid behavior or the antagonistic nature of said behavior.

@@

\section*{My Explanation}
I contend that an explanation of current U.S. foreign spending behavior must address both why it has a strong focus on technology and why this focus seems opposed to China. I argue that the U.S. is willing to spend aid on providing digital infrastructure because it allows them to build technology in U.S. fashion and thereby better protect U.S. technology market access to countries liable to Chinese technology influence. It is in the U.S.'s interest to attempt technological superiority over the Chinese, which is threatened by China's recent spreading of its technologies and companies to some recipient countries (see \cite{hass2021} for some suggestive anecdotal evidence).

If this is true, it should also be true that the U.S. is spending more in countries with more liberal internet governance since these are the countries that most allow for the use of U.S. technology. Further, these countries are likely not being invested in by China, whose aid is suspected on negatively affecting internet governance (e.g., \cite{triolo2020}; \cite{hillman2021}; \cite{u.s.departmentofstate2022}).

Internet governance was defined in the second phase of the World Summit on the Information Society (WSIS), a meeting led by the UN's International Telecommunication Union (ITU), which was held in Tunis, Tunisia in 2005. It is ``the development and application by governments, the private sector and civil society, in their respective roles, of shared principles, norms, rules, decision-making procedures, and programmes that shape the evolution and use of the Internet'' \nocite{worldsummitontheinformationsociety2005} (World Summit on the Information Society 2005, item 34). Essentially, internet governance refers to the way in which governments, firms, and citizens interact with the internet. The U.S. should be expected to allocate more aid to countries with higher measures of internet governance if they are truly bolstering U.S. firm access to technology markets.

\section*{Empirics}
Restating the implications of my argument, U.S. foreign aid should be directly related to recipient country internet governance since the U.S. is trying to build infrastructure that allows for an economically and politically liberal environment for U.S. technology to thrive. These same environments are most likely to exist in a country not financed by China, since China is sharing technology along with its money that could negatively affect recipient internet governance. Thus I will evaluate the following hypotheses:

\begin{align*}
    H_{1}&:\;\text{U.S. aid should be directly related to recipient internet governance}\\
    H_{2}&:\;\text{U.S. aid should be inversely related to Chinese aid}\\
\end{align*}
I test these hypotheses by regressing U.S. foreign aid on a measure of internet governance, Chinese aid and controls across 44 African countries between 2010 and 2017. The full set of countries includes: Algeria, Angola, Benin, Botswana, Burundi, Cabo Verde, Cameroon, Central African Republic, Chad, Comoros, Republic of the Congo, Cote d'Ivoire, Democratic Republic of the Congo, Djibouti, Egypt, Equatorial Guinea, Ethiopia, Gabon, Gambia, Ghana, Guinea, Guinea-Bissau, Kenya, Lesotho, Liberia, Madagascar, Malawi, Mali, Mauritania, Mauritius, Morocco, Mozambique, Namibia, Niger, Nigeria, Rwanda, Senegal, Sierra Leone, South Africa, Togo, Tunisia, Uganda, Zambia, and Zimbabwe.

@@

\subsection*{Data and Variables}
%internet governance
In operationalizing my theory, I measure internet governance using the Digital Society Project (DSP) index. The DSP aims to identify ``how people use social media as a political tool and to explore how political institutions and social media use interact,'' providing data from expert surveys that cover a range of topics such as censorship, disinformation, and monitoring (\cite{mechkova2022}). The DSP employs methodology designed by the Varieties of Democracy project (V-Dem, \cite{coppedge2022}) to try and estimate differences in expert opinion and knowledge.

@@

%controls
For controls, I include gross domestic product GDP per capita, an indicator for internet development, and a measure for political freedom as controls. Each of these phenomena are possible confounders, being theoretically related to at least one of the types of aid and internet governance.

@@

\subsubsection*{Table 3}
\begin{figure}[htbp]
    \includegraphics[scale=0.45]{Figures/summary.png}
\end{figure}

\pagebreak
A correlation matrix of the variables included in my regressions is given in Figure 2. As can be seen, there are a couple relatively strong relationships between the variables. The variable for regime type, Polity, has a correlation of 0.62 with the internet governance variable while logged GDP per capita has a correlation of 0.65 with the variable representing the percent of the population using the internet. While possible, I do not think that these correlations are high enough to warrant concerns over multicollinearity or the lack of linear independency in the data. Interestingly, logged U.S. Aid appears somewhat negatively correlated with logged GDP per capita and variable for the percent using the internet is somewhat positively correlated to that for internet governance. However, all of these correlations are relatively small and should not induce concerns for multicollinearity, although I did not conduct a formal test for multicollinearity.

@@

\pagebreak
\section*{Results}
Table 2 displays regression results from a model with and without an interaction between internet governance and logged Chinese foreign aid.
\begin{table}[!htbp] \centering 
  \caption{Logged U.S. Aid and Covariates with Two-way Fixed Effects and Clustered SE's on Country} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{2}{c}{Logged U.S. Aid} \\ 
\cline{2-3} 
 & Model 1 & Model 2 \\ 
\hline \\[-1.8ex] 
 Internet Governance & 0.021$^{***}$ & 0.021$^{***}$ \\ 
  & (0.008) & (0.008) \\ 
  & & \\ 
 Logged Chinese Aid & 0.006$^{*}$ & 0.006$^{*}$ \\ 
  & (0.003) & (0.003) \\ 
  & & \\ 
 Logged GDP per Capita & 0.045 & 0.045 \\ 
  & (0.471) & (0.472) \\ 
  & & \\ 
 Percent Using Internet & $-$0.013 & $-$0.013 \\ 
  & (0.009) & (0.009) \\ 
  & & \\ 
 Polity & 0.004 & 0.004 \\ 
  & (0.031) & (0.031) \\ 
  & & \\ 
 Internet Governance * Logged Chinese Aid &  & 0.00000 \\ 
  &  & (0.0002) \\ 
  & & \\ 
\hline \\[-1.8ex] 
Observations & 352 & 352 \\ 
R$^{2}$ & 0.038 & 0.038 \\ 
Adjusted R$^{2}$ & $-$0.140 & $-$0.144 \\ 
F Statistic & 2.370$^{**}$ (df = 5; 296) & 1.968$^{*}$ (df = 6; 295) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}
\pagebreak

The only covariates that appear statistically significant are internet governance and Chinese spending. Both internet governance and logged Chinese aid seem to increase logged U.S. aid on average when accounting for the other covariates. To gauge the substantive size of the coefficients, I plot the marginal effect of internet governance on logged U.S. aid in Figure 3 and the marginal effect of logged Chinese aid on logged U.S. aid in Figure 4, both from model 1 (seen in Table 2).

According to Table 2 and Figures 3 and 4, there is support for $H_1$. $H_2$ is contradicted by the evidence, meanwhile. However, I would be cautious about inferences from the results pertaining to logged Chinese aid as most of the values are zero, as can be seen in Figure 4. It is thus likely that the downward sloping line is overestimated due to all the zeros.

I also tested for an interaction between internet governance and logged Chinese aid, which was not part of my theory. The interaction term is not significant according to standard levels (p=0.05).

\pagebreak
Figure 3 shows the marginal effect of internet governance on logged U.S. foreign aid. The coefficient on the internet governance variable is 0.0206, implying that a one unit increase in a recipient's internet governance level is associated with an increase in U.S. aid by 2.08 percent on average, accounting for other covariates. This appears to be a substantively large effect.

@@

\section*{Discussion}
The support of $H_1$ but not $H_2$ indicate mixed results for my theory. However, it seems that robustness checks with mulitple other measures would be required to make more inferences about U.S. behavior, including for regime type and especially Chinese aid. The variable for Chinese aid contains mostly zeros with a few, large values that are qualified as outliers.

To the extent that my theory is supported, I contribute to the foreign aid literature by detailing a potentially new determinant for U.S. behavior. The internet and technology as a foreign policy and geopolitical issue will only continue to rise, and it's important that scholarly theories keep pace with contemporary observation. Secondly, some international relations literature has expressed concerns that China will undermine common tenets of the LIO, such as economic or political liberalism (e.g., \cite{weiss2021a}). While I do not study China's behavior here, my analysis indicate somewhat that the U.S. behaves as if China is indeed damaging political and economic liberalism, especially as it relates to the liberal use of the internet.

\section*{Conclusion}
In this article I argue that the U.S. is funding digital infrastructure in Africa to prevent the Chinese from building such infrastructure and closing market access to U.S. technology firms. I test the implications that U.S. foreign aid spending should be directly related to a measure for internet governance, or the rules and norms surrounding the internet, and inversely related to Chinese aid spending.

Analyzing 44 African countries from 2010-2017, I find mixed results for the theory, as U.S. aid indeed seems directly related to internet governance but also directly related to Chinese spending.

In future work, other measures for Chinese spending and influence would be critical to analyzing their digital infrastructure activities in Africa that go poorly reflected in aid data. The deriving of other implications and more falsification attempts are also necessary to test this explanation for recent U.S. spending behavior.
